---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#Introduction
The Susceptible-Infectious-Recovered (SIR) model is a classic compartmental model used to understand spread of infectious diseases in a population. This vignette demonstrates how to simulate and visualise the SIR model using the 'SIRr' package in R.

#Installation
To install the 'SIRr' package, you can use the following code:

```{r}
install.packages("SIRr")

devtools::install_github('Joao-PC-Filipe/SIRr')

```

#Usage
Firstly, load the 'SIRr' package and define the initial parameters for our simulation.

```{r}
library(SIRr)

# Define initial parameters
initial_state <- c(S = 0.99, I = 0.01, R = 0)
parameters <- c(beta = 0.3, gamma = 0.1)
times <- seq(0, 80, by = 1)

```

Next, we'll create an object of class SIRResult using the new() function:

```{r}

# Create an object of class SIRResult
sir_result_object <- new("SIRResult",
                         initial_state = initial_state,
                         times = times,
                         sir_model = function(time, state, parameters) {
                           with(as.list(c(state, parameters)), {
                             dS <- -beta * S * I
                             dI <- beta * S * I - gamma * I
                             dR <- gamma * I
                             return(list(c(dS, dI, dR)))
                           })
                         },
                         parameters = parameters)

```


Now, let's generate the SIR model simulation results using the generate() function:

```{r}

# Generate the SIR results
sir_result_object <- generate(sir_result_object)

```


Finally, we can visualize the simulation results using the create_sir_plot() function:

```{r}
# Plot the simulation results
sir_plot <- create_sir_plot(sir_result_object@output)
print(sir_plot)

```

#Conclusion
This vignette provided a brief overview of simulating and visualizing the SIR model using the SIRr package in R. For more details and advanced usage, please refer to the package documentation.







